Explore the SingleR results

### 2025-07-24 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/singler-results.Rmd
remove the really low-quality libraries, and a gitleaks spot to override

```{r}
merged_sce <- readRDS(sce_file)
# immediately remove assays we don't need for space
assay(merged_sce, "spliced") <- NULL
assay(merged_sce, "counts") <- NULL

# Ensure cell_id is correct
merged_sce$cell_id <- colnames(merged_sce)
```

@@

```{r}
singler_df <- singler_files |>
  purrr::map(readr::read_tsv) |>
  purrr::list_rbind(names_to = "library_id") |>
  dplyr::select(-delta.next, -labels) |>
  dplyr::mutate(
    # add cell id column for unique rows & joining
    cell_id = glue::glue("{library_id}-{barcodes}"),
    # recode NA -> "unknown_singler"
    pruned.labels = ifelse(
      is.na(pruned.labels),
      "unknown_singler",
      pruned.labels
    )
  )

>>>>

```{r}
merged_sce <- readRDS(sce_file)
# immediately remove assays we don't need for space
assay(merged_sce, "spliced") <- NULL
assay(merged_sce, "counts") <- NULL
reducedDim(merged_sce, "PCA") <- NULL

# Define libraries to remove
# See: https://github.com/AlexsLemonade/OpenScPCA-analysis/issues/1234#issuecomment-3113966395
remove_libraries <- c("SCPCL000124", "SCPCL001058")
keep_cells <- grep(
  paste(remove_libraries, collapse="|"), 
  colnames(merged_sce), 
  invert = TRUE,
  value = TRUE
)

merged_sce <- merged_sce[, keep_cells]
rm(keep_cells)
```

@@

```{r}
singler_df <- singler_files |>
  # remove libraries
  purrr::discard_at(remove_libraries) |>
  purrr::map(readr::read_tsv) |>
  purrr::list_rbind(names_to = "library_id") |>
  dplyr::select(-delta.next, -labels) |>
  dplyr::mutate(
    # add cell id column for unique rows & joining
    cell_id = glue::glue("{library_id}-{barcodes}"),
    # recode NA -> "unknown_singler"
    pruned.labels = ifelse(
      is.na(pruned.labels),
      "unknown_singler",
      pruned.labels
    )
  )
